Bird beak's elaboration and innovation

### 2022-04-21 Analysis/04-Figure1_with_ellipse_scalling_and_8D_histograms.Rmd
Update 04-Figure1_with_ellipse_scalling_and_8D_histograms.Rmd

tip_colours <- colour.palette(Ntip(tree_short))
names(tip_colours) <- names(sort(tip_order))

@@

tip_colours <- colour.palette(Ntip(tree_short))
names(tip_colours) <- names(sort(tip_order))

>>>>

tip_colours <- colour.palette(Ntip(tree_short))
names(tip_colours) <- names(sort(tip_order))
tip_colours_super_orders <- tip_colours
save(tip_colours_super_orders, file = "../Data/Processed/tip_colours_super_orders.rda")

@@

tip_colours <- colour.palette(Ntip(tree_short))
names(tip_colours) <- names(sort(tip_order))
tip_colours_orders <- tip_colours
save(tip_colours_orders, file = "../Data/Processed/tip_colours_orders.rda")
